**Title**

### 2018-07-20 manuscript_draft.Rmd
methods finished

---
title: "**Title**"
author: "$^{1}$Petr Capek*, $^{1}$Katherine Todd-Brown, $^{1}$Natalie Sadler, $^{1}$Nancy Hess, $^{1}$Kirsten Hofmockel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontfamily: mathpazo
fontsize: 11pt
bibliography: mint.bib
output: 
  word_document:
    fig_caption: true

@@

_$^{1}$Pacific Northwest National Laboratory, Environmental Molecular Sciences Laboratory, Richland, WA USA_

@@

## Material and Methods
###Experimental design
Microbial culture obtained from the soil (see later) was incubated in liquid batch culture microcosms at 24$^{\circ}C$ in the dark for five days under nine different experimental treatments. These treatments include three different organic substrates as a sole source of carbon for microbial culture and three different levels of microcosm structural complexity in fully factorial design. The three organic substrates were glucose, cellobiose and mixture of glucose, cellobiose and cellulose. The three levels of structural complexity were represented by **_??34 ml??_** incubation vials with liquid medium only (denoted as **"BROTH"** further in the text), with liquid medium and mixture of 2.7, 0.1 and 0.1 mm glass beads (5 g of 2.7 mm Biospec glass beads, 2 g of 1.0 mm Biospec glass beads and 1 g of 0.1 mm Next-Advanced glass beads; denoted as **"GLASS"** further in the text) and with liquid medium and glass wool (0.2 g of Pyrex fiber glass wool cutted to ~0.25 cm pieces; denoted as **"WOOL"** further in the text). All experimental treatments were replicated four times **_but this is probably not true since the sampling was destructive_**.

###Microbial culture
Microbial culture used in the experiment was obtained by imbibement of the **_??prosser soil?? (is it correct)_**, _short characteristic of soil_ ... with the growth medium. One gram of air dried soil was supplemented by the 10 ml of sterile Cellulose Degrader M9 Media (see later) with 6.25 ml of lysogeny broth. The final organic carbon concentration of added medium was ~40 mmol $l^{-1}$ (0.4 mmol $g(DW)^{-1}$). The soil with medium was incubated seven days at 24$^{\circ}C$ in dark. At the end of incubation, soil-medium suspension was shaken with ~ten 2.7 mm glass beats for ten minutes. The suspension was transferred to sterile flask and soil particles were allowed to settle down. The liquid phase was further transferred to new sterile flask and used to inoculate a microcosms.

@@

###DNA isolation and quantification
DNA was isolated before the start of the experiment, first, second and last day of incubation to quantify microbial biomass in the microcosms. Two ml of well mixed liquid solution was sampled and thorougly mixed with two ml of phosphate buffer. The final solution was centrifuged at 4,700 g for ten minutes at 4$^{\circ}C$ and pelet was separated from supernatant. Supernatant was anaylzed for protein concentration (see later). Pellet was resuspended in 0.5 ml and kept deep frozen (-80$^{\circ}C$) until the assay was conducted. 
Cell pelet was bead beated in ethanol solution for 5 minutes to lyse the cells. To isolate DNA from the cell lysate, DNeasy PowerSoil Kit (QIAGEN, Venlo, Netherland) was used. DNA concentration was measured by a Nanodrop meter **_(specification)_**. DNA concentration was conversed to microbial biomass carbon using several conversion factors published in literature (see Fig. 1)

@@

#colnames(tab1)<-c(" ", "Log Likelihood", "N", "$R^{2}$", "AIC")

kable(tab1, align='c', digits=c(0, 1, 0, 2, 1), "latex", booktabs=T, col.names = c(" ", "Log Likelihood", "N", "R^2^", "AIC"), caption = "Correspondence between measured resiration rate and respiration rate modeled by five different models (First order decay, Monod growth, two different Microbial Enzyme Models (MEM and MEND) and Metabolic Microbial Enzyme Model (MMEM)). Log Likelihood, coefficient of determination ($R^{2}$), Akaike Information Criterion (AIC) and the number of estimated parameters are reported. All models are calibrated against measured respiration rate only.") %>%
  kable_as_image()

@@

```{r Fig. 1, echo=FALSE, resultsw = 'asis', message=FALSE, warning=FALSE, fig.height=14, fig.width=9, fig.cap="_Distribution of microbial biomass carbon data as directly measured by the DNA or cellular protein concentration and calculated by different conversion factors published in the literature [@Baart2008; @Beck2018; @VanDuuren2013; @Marstorp2000, @Christensen1993; Christensen1993; @Yokoyama2017; @VanPutten1995; @Henriksen1996; @Hanegraaf2001]. Middle line corresonds to the median, lower and upper hinges to first and third quartile respectively, lower and upper whisker extends from lower and upper hinge to 1.5 time the interquartile range. Note that the x axis of both plots have different scales._"}

>>>>

---
title: "**Title**"
author: "^1^Petr Capek*, ^1^Katherine Todd-Brown, ^1^Natalie Sadler, ^1^Nancy Hess, ^1^Kirsten Hofmockel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontfamily: mathpazo
fontsize: 11pt
bibliography: mint.bib
output: 
  word_document:
    fig_caption: true

@@

_^1^Pacific Northwest National Laboratory, Environmental Molecular Sciences Laboratory, Richland, WA USA_

@@

## Material and Methods
###Experimental design
Microbial culture obtained from the soil (see later) was incubated in liquid batch culture microcosms at 24&deg;C in the dark for five days under nine different experimental treatments. These treatments include three different organic substrates as a sole source of carbon for microbial culture and three different levels of microcosm structural complexity in fully factorial design. The three organic substrates were glucose, cellobiose and mixture of glucose, cellobiose and cellulose. The three levels of structural complexity were represented by **_??34 ml??_** incubation vials with liquid medium only (denoted as **"BROTH"** further in the text), with liquid medium and mixture of 2.7, 0.1 and 0.1 mm glass beads (5 g of 2.7 mm Biospec glass beads, 2 g of 1.0 mm Biospec glass beads and 1 g of 0.1 mm Next-Advanced glass beads; denoted as **"GLASS"** further in the text) and with liquid medium and glass wool (0.2 g of Pyrex fiber glass wool cutted to ~0.25 cm pieces; denoted as **"WOOL"** further in the text). All experimental treatments were replicated four times **_but this is probably not true since the sampling was destructive_**.

###Microbial culture
Microbial culture used in the experiment was obtained by imbibement of the **_??prosser soil?? (is it correct)_**, _short characteristic of soil_ ... with the growth medium. One gram of air dried soil was supplemented by the 10 ml of sterile Cellulose Degrader M9 Media (see later) with 6.25 ml of lysogeny broth. The final organic carbon concentration of added medium was ~40 mmol l^-1^ (0.4 mmol g(DW)^-1^). The soil with medium was incubated seven days at 24&deg;C in dark. At the end of incubation, soil-medium suspension was shaken with ~ten 2.7 mm glass beats for ten minutes. The suspension was transferred to sterile flask and soil particles were allowed to settle down. The liquid phase was further transferred to new sterile flask and used to inoculate a microcosms.

@@

###DNA isolation and quantification
To quantify microbial biomass in the microcosms, DNA was isolated from samples before the start of the experiment, first, second and last day of incubation. The sampling was destructive. The whole volume of microcosm containing microbial cells was quantitatively transfered to 15 ml falcon tubes. Cell scraper was used to detach microbial cells from surface of microcosm or from glass beads/wool. Two ml of phosphate buffer was added and the final solution thoroughly mixed. The final solution was centrifuged at 4,700 g for ten minutes at 4&deg;C and pelet was separated from supernatant. Supernatant was anaylzed for protein concentration (see later). Pellet was resuspended in 0.5 ml and kept deep frozen (-80&deg;C) until the assay was conducted. 
Cell pelet was bead beated in ethanol solution for 5 minutes to lyse the cells. To isolate DNA from the cell lysate, DNeasy PowerSoil Kit (QIAGEN, Venlo, Netherland) was used. DNA concentration was measured by a Nanodrop meter **_(specification)_**. DNA concentration was conversed to microbial biomass carbon using several conversion factors published in literature (see Fig. 1)

###Cellular protein quantification
As a complementary method for microbial biomass quantification, protein concentration was assesed in cell lysate by bicinchoninic acid assay. **_(specification of spectrophotometer)_** was used to measure protein concentration. Alike DNA, protein concentration was conversed to microbial biomass carbon using several conversion factors published in literature (see Fig. 1)

###Extracellular protein concentration
Protein concentration was further assesed in the supernatant (see above). Before the analysis, supernatant was filtered through 10 kDa Supor membrane. Protein concentration was measured in >10 kDa fraction. This fraction is assumed to be dominated be extracellular enzymes produced by microbial cells. Extracellular enzymes are assumed to contain 46% of carbon [@Vrede2004].

###Mathematical description

@@

kable(tab1, align='c', digits=c(0, 1, 0, 2, 1), "latex", booktabs=T, escape=F, col.names = c(" ", "Log Likelihood", "N", "R^2^", "AIC"), caption = "Correspondence between measured resiration rate and respiration rate modeled by five different models (First order decay, Monod growth, two different Microbial Enzyme Models (MEM and MEND) and Metabolic Microbial Enzyme Model (MMEM)). Log Likelihood, coefficient of determination ($R^{2}$), Akaike Information Criterion (AIC) and the number of estimated parameters are reported. All models are calibrated against measured respiration rate only.") %>%
  kable_as_image()

```{r Tab. 2, echo=FALSE, fig.width=130, message=FALSE, warning=FALSE, results='asis'}
# tab2a<-rbind(monod_all_results2$ll_r, mem_all_results2$ll_r,
#              mend_all_results2$ll_r, mmem_all_results2$ll_r,
#              monod_all_results4$ll_r, mem_all_results4$ll_r,
#              mend_all_results4$ll_r, mmem_all_results4$ll_r,
#              monod_all_results5$ll_r, mem_all_results5$ll_r,
#              mend_all_results5$ll_r, mmem_all_results5$ll_r,
#              monod_all_results6$ll_r, mem_all_results6$ll_r,
#              mend_all_results6$ll_r, mmem_all_results6$ll_r)
# tab2a[tab2a[,3]<0,"rsq"]<-c(0)
#  
# tab2b<-rbind(monod_all_results2$ll_Cmic, mem_all_results2$ll_Cmic,
#              mend_all_results2$ll_Cmic, mmem_all_results2$ll_Cmic,
#              monod_all_results4$ll_Cmic, mem_all_results4$ll_Cmic,
#              mend_all_results4$ll_Cmic, mmem_all_results4$ll_Cmic,
#              monod_all_results5$ll_Cmic, mem_all_results5$ll_Cmic,
#              mend_all_results5$ll_Cmic, mmem_all_results5$ll_Cmic,
#              monod_all_results6$ll_Cmic, mem_all_results6$ll_Cmic,
#              mend_all_results6$ll_Cmic, mmem_all_results6$ll_Cmic)
# tab2b[tab2b[,3]<0,"rsq"]<-c(0)
#  
# tab2<-cbind(tab2a, tab2b)
#  
# write.csv(tab2, "./tab2.csv")

tab2<-read.csv("tab2.csv")

#colnames(tab1)<-c("_Log Likelihood_", "_N_", "_R^{2}_", "_AIC_")
# rownames(tab2)<-c("Monod growth", "MEM", "MEND", "MMEM","Monod growth", "MEM", "MEND", "MMEM","Monod growth", "MEM", "MEND", "MMEM","Monod growth", "MEM", "MEND", "MMEM")
#write.csv(tab1, "./tab1.csv")

kable(tab2, align='c', digits=c(0, 1, 0, 2, 1, 1, 0, 2, 1), "latex", escape=F, booktabs=T, col.names = c(" ", "Log Likelihood", "N", "R^2^", "AIC","Log Likelihood", "N", "R^2^", "AIC"), caption = "Correspondence between measured resiration rate and respiration rate modeled by five different models (First order decay, Monod growth, two different Microbial Enzyme Models (MEM and MEND) and Metabolic Microbial Enzyme Model (MMEM)). Log Likelihood, coefficient of determination ($R^{2}$), Akaike Information Criterion (AIC) and the number of estimated parameters are reported. All models are calibrated against measured respiration rate only.") %>%
  add_header_above(c(" " = 1 ,"Respiration rate" = 4, "Microbial biomass" = 4))  %>%
  group_rows("Beck et al., 2018 (DNA ~ 0.9% $C_{MB}$)", 1 , 4) %>%
  group_rows("Median of DNA abundance across studies (DNA ~ 2.39% $C_{MB}$)", 5 , 8) %>%
  group_rows("Beck et al., 2018 (Protein ~ 60%% $C_{MB}$)", 9 , 12) %>%
  group_rows("Hanegraaf and Muller, 2001 (Protein ~ 182%% $C_{MB}$)", 13 , 16) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, font_size = 7) %>%
  kable_as_image()

@@

```{r Fig. 1, echo=FALSE, resultsw = 'asis', message=FALSE, warning=FALSE, fig.height=10, fig.width=7, fig.cap="_Distribution of microbial biomass carbon data as directly measured by the DNA or cellular protein concentration and calculated by different conversion factors published in the literature [@Baart2008; @Beck2018; @VanDuuren2013; @Marstorp2000, @Christensen1993; Christensen1993; @Yokoyama2017; @VanPutten1995; @Henriksen1996; @Hanegraaf2001]. Middle line corresonds to the median, lower and upper hinges to first and third quartile respectively, lower and upper whisker extends from lower and upper hinge to 1.5 time the interquartile range. Note that the x axis of both plots have different scales._"}
